Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
yny

\dropcap{W}ater exchange is essential as a living cell adapts to its environment over a wide range of timescales \cite{CadartVenkovaRechoEtAl2019_NaturePhys,AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.  
%
%Water permeation across the cell membrane due to an osmotic shock has been well studied \cite{AlbertsMolecularBiology}. 
Recent findings confim that both osmotic and mechanical stresses contribute to significant water permeation for cells to migrate under strong confinement \cite{JiangSun2013_BJ,StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio of a migrating cell. 
While stress-induced release of messengers in cells has been well studied \cite{Wan2008_PNAS, ForsythWan2011_PNAS,Russell-PuleriPazAdams2016_AJHCP,ZhangShenHoganBarakatMisbah2018_BJ,GordonShimmelFrye2020_FP},
%osmotic effects on cellular dynamics have been well studied \cite{AlbertsMolecularBiology}, 
mechanically induced water permeation is often associated with membrane poration or rupture under extreme stresses \cite{RazizadehNikfarPaulLiu2020_BJ}. In this work we use modeling and state-of-the-art numerical simulations to show that the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the lipid bilayer membrane. 
%
%
%One of the most direct ways to induce water permeation across cell membranes is to impose an osmotic shock }.
%
%A gradient in the osmotic stress across the cellular membrane is the most direct way to induce water permeation, yet 
%%
%%In response to external stimuli, cells move, deform, and release signaling molecules, such as ATP in red blood cells \cite{ZhangShenHoganBarakatMisbah2018_BJ} and cyclooxygenase-2 in endothelial cells \cite{Russell-PuleriPazAdams2016_AJHCP}. 
%%
%%Water permeation is often neglected in such release processes, yet 
%%
%recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for tumor cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio over time. 
%
%
%To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the hydrodynamics of a semi-permeable vesicle in various configurations.

@@

The lipid bilayer membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. 
%
%In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient  to neutralize the osmolarity. 
%
Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid composition \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, and the hydration of the membrane \cite{MarrinkBerendsen1994_JPhysChem}. In the red blood cell membrane, aquaporin-1 channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB,BhatiaRobinsonDimova2020_SoftMatt}. 
%
%The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and deformation. Under a strong confinement (such as going through a microcapillary or submicron slit),  the transmembrane water flow may have comparable contributions from both osmotic and mechanical stresses \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.  
Molecular dynamic (MD) 
%and coarse-grained (CG) MD 
simulations show that a stretched RBC membrane may porate when membrane tension reaches the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein), giving rise to enhanced membrane permeability to both water and macromolecules. Consequently, as long as the lipid bilayer membrane remains intact (no poration or rupture), RBCs and vesicles are assumed to be of the same volume throughout experiments of durations no longer than tens of minutes. 
%
%membrane poration is inevitable when membrane tension is of the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein). 
%%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
%Thus an important outstanding question in stress-induced ATP release of highly deformed RBCs is if there is any transmembrane flow when RBCs release ATP as they experience large
%mechanical load due to confinement or large shear stress?  To address such question, the first step we take is to focus on the permeable water flux induced by mechanical stress.
%%
%%RBCs are known to release ATP under large deformation and microfluidic experiments have been used to study the correlation between RBC deformation and ATP release \cite{Wan2008_PNAS,ForsythWan2011_PNAS,ZhangShenHoganBarakatMisbah2018_BJ}.
%%
%%Why is it interesting to study the dynamics of a semi-permeable membrane induced by mechanical stress/confinement?
%%
%%The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
%%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
Under what condition is this a good assumption? What is the dynamic consequence when permeable water flux/eflux affects the membrane hydrodynamics?
To answer these questions, we investigate the balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement. 
%Specifically our numerical simulations yield the quantification of the time scale and length scale over which water permeation becomes important.

 In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}. Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}. When trapped in a microfluidic channel, an osmotic shock induces 
 vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.  
 In microfluidic experiments, it is challenging to keep a freely suspended vesicle in a steady flow for more than a few hours. It is also difficult to quantify the vesicle area/volume ratio accurately. Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses. In the absence of an osmotic gradient, we first show that a freely suspended semipermeable vesicle behaves differently from an impermeable vesicle over a long time. Next we show that, at normal physiological conditions, the permeable water flow can be amplified by extreme confinement and results in observable change in both vesicle hydrodynamics and reduced area.  These results will shed light on the dynamic aging process of living cells that constantly go through flows and constrictions over a period of days.

%
%\paragraph{Literature to maybe cite}
%\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
%happens in regions where proteins congregate and this can lead to
%semi-permeability?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htp]
  \centering
  \includegraphics[width=0.45\textwidth]{figures/schematic.pdf}
  \caption{\label{fig:sketch} Schematics showing the effects of
  semipermeability on vesicle hydrodynamics in various configurations.
  The slipper in (a) is the steady-state shape of a semi-permeable
  vesicle in a Poiseuille flow.}
\end{figure}

\section*{Formulation}
We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:sketch}.
To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane ($\gamma$) with an outward normal $\nn$.
On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
and the membrane velocity $\dot{\bf x}$ \cite{yao-mor2017}:
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
is the arclength along the membrane, see figure~\ref{fig:sketch}. Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s. Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution 
($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-2}:10^{-6}$.  Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.
In the following we will explore both.

@@

In experiments vesicle under shear flows are measured for a minute (chapter 19 in \cite{Dimova2020_GVB}), a duration over which vesicle can be assumed impermeable \cite{AbkarianViallat2005_BJ}. Our simulations of a semi-permeable vesicle
in these flows show that water permeability may lead to different vesicle hydrodynamics over a time scale of 10 to 100 minutes. {\bf YNY: is this correct? The shear flow results seem to suggest that the permeability may lead to change in area in less than a second???}
For vesicles in a narrow micro-fluidic channel, the typical time scale is of $ms$ \cite{abk-fai-sto2006}. Our simulations show that strong confinement can lead to amplification of water permeability at such short time scale.
%
%all vesicles have a length
%$L$, but the area is not conserved because of semi-permeability. We vary
%the initial vesicle reduced area, the permeability rate, and the flow
%rate. For all simulations, the bending modulus is $10^{-19}J$.

@@

We consider a semi-permeable vesicle in a planar shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability
rates $\beta$ and shear rates $\dot{\gamma}$. 
When $\beta=0$ (impermeable case), a vesicle's reduced area
and viscosity contrast determine whether it tank treads or
tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. 
Focusing on semi-permeable vesicles with no viscosity contrast, 
we find that a semi-permeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics, similar to the case of  an impermeable vesicle.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Narrow Channel (Stenosis)}
Cells experience stretching and release messengers when they pass through capillary vessels \cite{Wan2008_PNAS,ForsythWan2011_PNAS,Pak2015_PNAS}.
Many cells exhibit extraordinary flexibility as they go through narrow channels \cite{AuStoreyMoore2016_PNAS}, and adjustment of area to volume ratio may be a key factor for a successful passage.
Here we quantify the effect of water permeability on a vesicle going through a stenosis (a long microfluidic channel with a width smaller than the cell radius).
Based on the findings in 
%We consider the effect of stenosis on a semi-permeable vesicle. Inspired
%by an experiment that measures the effects of cells on the dynamical
%pressure-drop variations along a micrometer-sized
\cite{abk-fai-sto2006}, we first examine the effect of
semi-permeability on the pressure fluctuation across a stenosed
geometry. In this experiment, a pressure drop is used to squeeze a
red blood cell (RBC) through a constriction with diameter $5\mu$m and
length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow rate is chosen so that
the residency time of the RBC in the constriction agrees with the
experimental results. When the RBC enters the channel, an increase in the pressure drop is required to maintain a constant flow
rate, and the difference in the pressure drop is called the excess
pressure.

We consider both an impermeable and semi-permeable vesicle with initial
reduced area $\alpha = 0.65$ passing through a long narrow channel and
compute the excess pressure as a function of vesicle position in the
channel, see Figure~\ref{fig:stenosisComposite}(c). A constant
Poiseuille velocity with a maximum value of $1000\mu$m/s is maintained
at the inlet and outlet. The impermeable case agrees with experimental
results in Figure 3 of~\cite{abk-fai-sto2006}, and the results indicate
that less excess pressure is required to maintain a constant flow rate
when the vesicle is semi-permeable. First we note that the vesicle
deflates from the beginning due to the high flow velocity, consistent
with the results for a vesicle in a Poiseuille flow in open space. As
the vesicle enters the stenosis channel, the vesicle continues to
deflate in the front even though we observe influx (red segment) at
various rear locations in the membrane.  These results are consistent
with the results in~\cite{Pak2015_PNAS} where the membrane tension is
sufficiently large in the front of the vesicle as it goes through a
constrictive channel.

Our simulations indicate the semi-permeability does affect the excess
pressure, and the vesicle's reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of triple the length, and we observe that the reduced
area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
\begin{itemize}
  \item In plot (a), flow rate is $1000 \mu m/s$ and residency time is
    $t_R = 45.6 \times 10^{-2}$ s.
  \item In plot (b), flow rate is $8.4 \mu m/s$ and residency time is
    $t_R =  16.2$ s.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
Squeezing a cell or an elastic vesicle through a slit in microfluidics has gained popularity for its application in stress-induced release of macromolecules
\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}. RBCs go through submicron slits many times during their lifetime, and such process selects healthy, flexible RBCs to survive \cite{wu2015critical,LuPeng2019_PoF}.
Here we investigate the role of membrane permeability to water when a semi-permeable vesicle is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
where the width of the channel gradually decreases from $16\mu$m to $1.6\mu$m. The channel then immediately opens
again to $16\mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant maximum flow
rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
= 0.65$ that spans $10\mu$m of the total channel width and investigate
the effects of the membrane permeability to water and the maximum flow velocity on whether a vesicle can successfully pass through the slit. 
We color the vesicle according to the sign of its flux---red for influx and blue for efflux.

>>>>

\dropcap{W}ater exchange is essential for a living cell to adapt to its environment over a wide range of timescales \cite{CadartVenkovaRechoEtAl2019_NaturePhys,AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}.  
%
%Water permeation across the cell membrane due to an osmotic shock has been well studied \cite{AlbertsMolecularBiology}. 
Recent findings confim that both osmotic and mechanical stresses contribute to significant water permeation for cells to migrate under strong confinement \cite{JiangSun2013_BJ,StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio of a migrating cell. 
While stress-induced release of messengers in cells has been well studied \cite{Wan2008_PNAS, ForsythWan2011_PNAS,Russell-PuleriPazAdams2016_AJHCP,ZhangShenHoganBarakatMisbah2018_BJ,GordonShimmelFrye2020_FP},
%osmotic effects on cellular dynamics have been well studied \cite{AlbertsMolecularBiology}, 
mechanically induced water permeation is often associated with membrane poration or rupture under extreme stresses \cite{HarmanBertrandJoos2017_CJP,RazizadehNikfarPaulLiu2020_BJ}. In this work we use modeling and direct numerical simulations to show that, 
over the appropriate time scales or under strong confinement,
the intrinsic membrane permeability to water can give rise to significantly distinct hydrodynamics of a semipermeable vesicle without poration or rupture in the lipid bilayer membrane. 
%
%
%One of the most direct ways to induce water permeation across cell membranes is to impose an osmotic shock }.
%
%A gradient in the osmotic stress across the cellular membrane is the most direct way to induce water permeation, yet 
%%
%%In response to external stimuli, cells move, deform, and release signaling molecules, such as ATP in red blood cells \cite{ZhangShenHoganBarakatMisbah2018_BJ} and cyclooxygenase-2 in endothelial cells \cite{Russell-PuleriPazAdams2016_AJHCP}. 
%%
%%Water permeation is often neglected in such release processes, yet 
%%
%recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for tumor cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio over time. 
%
%
%To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the hydrodynamics of a semi-permeable vesicle in various configurations.

@@

The lipid bilayer membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. 
%
%In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient  to neutralize the osmolarity. 
%
Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, lipid composition \cite{OlbrichRawiczNeedhamEtAl2000_BJ}, and the hydration of the membrane \cite{MarrinkBerendsen1994_JPhysChem}. In the red blood cell membrane, aquaporin-1 channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB,BhatiaRobinsonDimova2020_SoftMatt}. 
%
%The swelling/shrinking of a cell is inevitably coupled to changes in membrane tension and deformation. Under a strong confinement (such as going through a microcapillary or submicron slit),  the transmembrane water flow may have comparable contributions from both osmotic and mechanical stresses \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.  
Molecular dynamic (MD) 
%and coarse-grained (CG) MD 
simulations show that a stretched RBC membrane porates when the membrane tension reaches the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein), giving rise to enhanced membrane permeability to both water and macromolecules. Consequently, as long as the lipid bilayer membrane remains intact (no poration or rupture), RBCs and vesicles are assumed to be of the same volume throughout experiments of durations no longer than tens of minutes. 
%
%membrane poration is inevitable when membrane tension is of the order of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein). 
%%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
%Thus an important outstanding question in stress-induced ATP release of highly deformed RBCs is if there is any transmembrane flow when RBCs release ATP as they experience large
%mechanical load due to confinement or large shear stress?  To address such question, the first step we take is to focus on the permeable water flux induced by mechanical stress.
%%
%%RBCs are known to release ATP under large deformation and microfluidic experiments have been used to study the correlation between RBC deformation and ATP release \cite{Wan2008_PNAS,ForsythWan2011_PNAS,ZhangShenHoganBarakatMisbah2018_BJ}.
%%
%%Why is it interesting to study the dynamics of a semi-permeable membrane induced by mechanical stress/confinement?
%%
%%The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
%%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
Under what condition is this a good assumption? Do vesicles conserve volume over hours under flow? What is the dynamic consequence when water influx/efflux affects the membrane hydrodynamics?
To answer these questions, we investigate the balance between hydrodynamics, tension and elasticity of a semipermeable membrane under various flowing conditions and confinement. 
%Specifically our numerical simulations yield the quantification of the time scale and length scale over which water permeation becomes important.

% In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
In microfluidic experiments, it is challenging to keep a freely suspended RBC or vesicle in a steady flow for more than a few hours. It is also difficult to quantify the vesicle area/volume ratio accurately. Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses. 
Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}. Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}. When trapped in a microfluidic channel, an osmotic shock induces 
 vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.  In the absence of an osmotic gradient, we first show that a freely suspended semipermeable vesicle behaves differently from an impermeable vesicle over a long time. Next we show that, at normal physiological conditions, the permeable water flow can be amplified by extreme confinement and results in observable change in both vesicle hydrodynamics and reduced area.  These results will shed light on the dynamic aging process of living cells that constantly go through flows and constrictions over a period of days.

%
%\paragraph{Literature to maybe cite}
%\cite{ali-ovr-ran2020} show how beading can occur on nanotubes. This
%happens in regions where proteins congregate and this can lead to
%semi-permeability?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htp]
  \centering
  \includegraphics[width=0.45\textwidth]{figures/schematic.pdf}
  \caption{\label{fig:sketch} Schematics showing the effects of
  semipermeability on vesicle hydrodynamics in various configurations.
  The slipper in (a) is the steady-state shape of a semi-permeable
  vesicle in a Poiseuille flow.}
\end{figure}
\section*{Formulation}
We consider a two-dimensional semi-permeable vesicle (permeable only to water) suspended in a viscous fluid, see figure~\ref{fig:sketch}.
To focus on the effect of water flow on vesicle hydrodynamics in various conditions, we assume the fluid is the same inside and outside the vesicle membrane.
%($\gamma$) with an outward normal $\nn$.
On the membrane the permeable water flux gives rise to a difference between the fluid velocity ${\bf u}({\bf x}\in \gamma)$
and the membrane velocity $\dot{\bf x}$ \cite{yao-mor2017}:
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\gamma$ denotes the membrane boundary with an outward normal $\nn$, $k_w$ is the water permeability, $R$ is the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute concentration (mol/volume),
and $\ff_\mathrm{mem}$ is the membrane stress that consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$
is the arclength along the membrane, see figure~\ref{fig:sketch}. Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell membranes \cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration experiments \cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s. Assuming that the membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension $10^{-3}$N/m (one tenth of the lysis tension) and a characteristic length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$) and elastic stress contribution 
($v_\mathrm{e}$) to the permeable water flow can be scaled to $v_\mathrm{o}$ as $v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=1:10^{-2}:10^{-6}$.  Furthermore, we note that in the absence of an osmotic stress, the water permeable flow can be significant when the membrane tension is large due to the external stress such as the hydrodynamics stress due to an external flow and/or due to confinement.
In the following we will explore both.

@@

In experiments vesicle under shear flows are measured for a minute (chapter 19 in \cite{Dimova2020_GVB}), a duration over which vesicle can be assumed impermeable \cite{AbkarianViallat2005_BJ}. Our simulations of a semi-permeable vesicle
in these flows show that water permeability may lead to different vesicle hydrodynamics over a time scale of 10 to 100 minutes. 
%{\bf YNY: is this correct? The shear flow results seem to suggest that the permeability may lead to change in area in less than a second???}
For vesicles in a narrow micro-fluidic channel, the typical time scale is of $ms$ \cite{abk-fai-sto2006}. Our simulations show that strong confinement can lead to amplification of water permeability at such short time scale.
%
%all vesicles have a length
%$L$, but the area is not conserved because of semi-permeability. We vary
%the initial vesicle reduced area, the permeability rate, and the flow
%rate. For all simulations, the bending modulus is $10^{-19}J$.

@@

We consider a semi-permeable vesicle in a planar shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$ with different permeability  $\beta$ and shear rates $\dot{\gamma}$. 
When $\beta=0$ (impermeable case), a vesicle's reduced area
and viscosity contrast determine whether it tank treads or
tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. 
Focusing on semi-permeable vesicles with no viscosity contrast, 
we find that a semi-permeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics, similar to the case of  an impermeable vesicle.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Narrow Channel (Stenosis)}
Cells experience stretching and release messengers when they pass through capillary vessels \cite{Wan2008_PNAS,ForsythWan2011_PNAS,Pak2015_PNAS}.
Many cells exhibit extraordinary flexibility as they go through narrow channels \cite{AuStoreyMoore2016_PNAS}, and adjustment of area to volume ratio may be a key factor for a successful passage.
Here we quantify the effect of water permeability on a vesicle going through a stenosis (a long microfluidic channel with a width smaller than the cell radius).
Based on the findings in 
%We consider the effect of stenosis on a semi-permeable vesicle. Inspired
%by an experiment that measures the effects of cells on the dynamical
%pressure-drop variations along a micrometer-sized
\cite{abk-fai-sto2006}, we first examine the effect of
semi-permeability on the pressure fluctuation across a stenosed
geometry. In this experiment, a pressure drop is used to squeeze a
red blood cell (RBC) through a constriction with diameter $5\mu$m and
length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} = 1000 \mu$m/s is chosen so that
the residency time of the vesicle  in the stenosis channel $t_R \approx 0.5$ s agrees with the
experimental results \cite{abk-fai-sto2006}. When the RBC enters the channel, an increase in the pressure drop is required to maintain a constant flow
rate, and the difference in the pressure drop is called the excess
pressure.

We consider both an impermeable and semi-permeable vesicle with initial
reduced area $\alpha = 0.65$ passing through a long narrow channel and
compute the excess pressure as a function of vesicle position in the
channel, see Figure~\ref{fig:stenosisComposite}(c). A 
Poiseuille flow with a maximum value of $1000 \mu$m/s is maintained
at the inlet and outlet. The impermeable case agrees with experimental
results in Figure 3 of~\cite{abk-fai-sto2006}. Our simulations show that
less excess pressure is needed to drive a semi-permeable vesicle through the closely-fit channel.
Once in the channel, the vesicle takes a bullet shape with maximum tension in the front and minimum tension in the back (see Figure~\ref{fig:stenosisComposite}(a)),
consistent with earlier results \cite{Pak2015_PNAS,HarmanBertrandJoos2017_CJP}.

Figure~\ref{fig:stenosisComposite}(d)) shows
that the vesicle
deflates from the beginning due to the high flow velocity, consistent
with the results for a vesicle in a Poiseuille flow in open space. As
the vesicle enters the stenosis channel, it continues to
deflate in the front even though we observe influx (red segment) at
various rear locations in the membrane. Overall, the vesicle loses about 6.1\% of its initial total water at a constant rate as shown in
Figure~\ref{fig:stenosisComposite}(d).  Thus we expect that a larger amount of deflation is possible
if the vesicle is inside a longer stenosis: we consider a vesicle passing
through a channel of triple the length in
Figure~\ref{fig:stenosisComposite}(b) with $U_{max}=8.4 \mu$m/s, and we observe that vesicle stays inside the stenosis  for a residence time $t_R=16.2$ seconds and the reduced
area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
%\begin{itemize}
%  \item In plot (a), flow rate is $1000 \mu m/s$ and residency time is
%    $t_R = 45.6 \times 10^{-2}$ s.
%  \item In plot (b), flow rate is $8.4 \mu m/s$ and residency time is
%    $t_R =  16.2$ s.
%\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
Squeezing a cell or an elastic vesicle through a slit in microfluidics has gained popularity for its application in stress-induced release of macromolecules
\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}. RBCs go through submicron slits many times during their lifetime, and such process selects healthy, flexible RBCs to survive \cite{wu2015critical,LuPeng2019_PoF}.
Here we investigate the role of membrane permeability to water when a semi-permeable vesicle is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
where the width of the channel gradually decreases from $16 \mu$m to $1.6 \mu$m. The channel then immediately opens
again to $16 \mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant maximum flow
rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
= 0.65$ that spans $10 \mu$m of the total channel width and investigate
the effects of the membrane permeability to water and the maximum flow velocity on whether a vesicle can successfully pass through the slit. 
We color the vesicle according to the sign of its flux---red for influx and blue for efflux.
